---
title: "Exam 3"
author: "Kavya Sethi"
date: "7/8/2021"
output: 
  word_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Clear the evironment


```{r}
rm(list=ls(all=TRUE))
```

# 2. Female Labor Force Participation download

Googled the indicator and got https://data.worldbank.org/indicator/SL.TLF.CACT.FE.ZS as the website. 


```{r}
library(WDI)

female_lfp = WDI(country = "all", indicator = c("SL.TLF.CACT.FE.ZS"),
  start = 2010, # start of Female Labor Force Data 
  end = 2015, # end of of Female Labor Force Data 
  extra = FALSE, cache = NULL)
```

# 3. Rename female labor force participation variable 

```{r}
library(data.table) 
setnames(female_lfp,"SL.TLF.CACT.FE.ZS", "flfp",skip_absent = TRUE)
```

# 4. Collapse female_lfp by the mean value for flfp for each country.

```{r}
#collapsed_flfp <-  
 #female_lfp

#collapsed_flfp <-  
 #female_lfp %>% 
  #group_by(country,iso2c) %>% 
  #ummarize(flfp = mean(flfp, na.rm=TRUE))

#collapsed_flfp$year = NULL # Removes year from dataframe

```



# 5. Show participation rates that are less than 15% 


```{r}
library(dplyr)

#filter(collapsed_flfp,flfp <= 15)
```



# 6. World Map presenting collapsed_flfp data. 

## Must first run necessary libraries. 
```{r}
library(rio) 
library(tidyverse)

library(googlesheets4) 
library(labelled) 
library(data.table)

library(varhandle) 
library(ggrepel) 
library(geosphere) 
library(rgeos)

library(viridis)

library(mapview)
library(rnaturalearth)
library(rnaturalearthdata)
library(devtools)

library(remotes)

library(raster)

library(sp)

library(sf)

library(Imap)


library(rnaturalearthhires)
library(ggsflabel)
```


## Loading/Transforming Shapefiles

Must first load shape file of the world. 

```{r}
world_borders <- st_read('/Users/kavyasethi/Documents/DataScience/Module 11 - GIS/world border shape files')
```

Now transform shapefiles into WGS84 format. 

```{r}
borders <-st_transform(world_borders, "+proj=longlat +ellps=WGS84 +datum=WGS84")

# remove world_boarders cus no longer needed. 
rm(world_borders)
```


## Fix Data for Map 

Drop NAs for Map 

```{r}
#collapsed_flfp = na.omit(collapsed_flfp,select(flfp))
```

## Now merge tables of collapsed_flfp and borders to get lat/long 

```{r}
library(data.table) 
#setnames(collapsed_flfp,"iso2c","ISO2")

#merged_data = left_join(borders, collapsed_flfp, by=c("ISO2"))

```



## Now get map of the world

```{r}
world <- ne_countries(scale = "large", returnclass = "sf")
```


## Now Map the Viridis Color Map


```{r}
#collapsed_flfp_map = ggplot() +
#geom_sf(data = world) +
#geom_sf(data = merged_data, aes(fill=`flfp`)) + scale_fill_viridis(option = "viridis") +
#ggtitle("female labor force participation, 2010-2015") + theme(plot.title = element_text(hjust = 0.5)) +
#theme_void()

#print(collapsed_flfp_map) Printing was taking to long to load. 

#ggsave(collapsed_flfp_map, filename = "femalelaborforceworldmap.png", width = 6.5, height = 6)
```


# 7. The southern region of Africa has the largest cluster of yellow (percentage of female labor force participation)


# 8. Use R to show cluster of yellow states.

The instruction don't detail that it only has to be the cluster that shows up. So looking at color scale, we see upward of 75% are the yellowish states.

```{r}
library(dplyr)

#filter(collapsed_flfp,flfp >= 75)
```



# 9. Shiny components 

Shiny has three main components: UI, Server, Excecution 

The Subcomponents of UI: Input and Output




# 10. Pull Mike Denly's PDF 



```{r}
library(pdftools)
library(tidyr) 
library(tidytext) 
library(dplyr) 
library(stringr) 
library(ggplot2)

denlypdf = pdf_text("https://pdf.usaid.gov/pdf_docs/PA00TNMJ.pdf")

```


# 11. Convert pdf character vector to dataframe 



```{r}
armeniatext=as.data.frame(denlypdf)
armeniatext$page=c(1:59)
```



# 12. Tokenize and Remove Stop Words 
R keeps giving me error for code below. 
Error: by must be supplied when x and y have no common variables. ℹ use by = character()` to perform a cross-join.
I am unable to fix the error. I searched online and in notes. I literally copied and pasted the code from the notes. Its not fixable.
I just put the code down that I know would work from the basis of the notes. Also the notes pdf for harrypoter/trump analysis wasn't live, so I was not able to truly test the concept. 

```{r}

#armeniatext=armeniatext %>% 
  #unnest_tokens(word, text)

#data(stop_words)
#armeniatext=armeniatext %>% 
  #anti_join(stop_words)

```


# 13 Figure Out the top 5 Most Common word in report. 
Continued Error because of previous error. I just put down the code of how to do it. 

```{r}
#freq <- armeniatext %>% 
  #count(word, sort = TRUE)
#head(freq)

```


# 14 Load Billboard Page 


```{r}
library(rvest)
library(dplyr)


hot100exampage <- "https://www.billboard.com/charts/hot-100" 
hot100exam <- read_html(hot100exampage)

hot100exam
```

# 15 Identify All the nodes in Webpage

```{r}
body_nodes <- hot100exam %>% 
  html_node("body") %>% 
  html_children()
body_nodes

head_nodes <- hot100exam %>% 
  html_node("head") %>% 
  html_children()
head_nodes
```



# 16 Billboard Ranking This Week including last week. 


```{r}
rank <- hot100exam %>%
rvest::html_nodes('body') %>% 
xml2::xml_find_all("//span[contains(@class,
                   'chart-element__rank__number')]") %>%
rvest::html_text()

artist <- hot100exam %>%
rvest::html_nodes('body') %>% 
xml2::xml_find_all("//span[contains(@class,
                   'chart-element__information__artist')]") %>%
rvest::html_text()

title <- hot100exam %>% 
rvest::html_nodes('body') %>% 
xml2::xml_find_all("//span[contains(@class,
                   'chart-element__information__song')]") %>%
rvest::html_text()

lastweek <- hot100exam %>% 
rvest::html_nodes('body') %>% 
xml2::xml_find_all("//span[contains(@class,
                   'chart-element__meta text--center color--secondary text--last')]") %>%
rvest::html_text()



chart_df <- data.frame(rank, artist, title,lastweek)

knitr::kable(
  chart_df %>% head(10))

```








# 17. GitHUB repo link 

https://github.com/kavyasethi14/KavyaSethi_GOVF355M_Exam_3.git 



# 18. Rmarkdwon keeps giving me an error 

I included the pictures in this pdf. So I had to comment every r chunk that included the collapsed_flfp. I know it works when I individually run the chunks, but rmarkdown isn't letting it load. 

[proof of filter working on question 5](proofoffilterworking.png)


[error on collapsed_flfp](Rmarkdownerror.png)

Attached proof will also be uploaded to github
I also exported all the dataframes from where the error occured. Will uplaod to github. I also exported the map, will uplaod to github. 



